Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-17 paper/ms.tex
Add gas scale height discussion

{\bf We measured the initial scale height of the gas disk in a bin extending from
$R=8\,\textrm{kpc}$ to $R=8.5\,\textrm{kpc}$. The vertical profile is well-fit
by a Gaussian with a scale height of $97\,\textrm{pc}$. This is somewhat lower
than the observed value in the HI disk of $\sim200\,\textrm{kpc}$
\citep{1995ApJ...448..138M}.}

>>>>

{\bf We measured the initial scale height of the atomic gas disk in a bin
extending from $R=7.5\,\textrm{kpc}$ to $R=8.5\,\textrm{kpc}$. The initial
vertical profile is well-fit by a Gaussian with a scale height of
$110\,\textrm{pc}$. At $t=1\,\textrm{Gyr}$, the vertical profile in the same
radial bin is better fit by an exponential profile with scale height of
$74\,\textrm{pc}$. These are somewhat lower than the observed value in the HI
disk of $\sim200\,\textrm{kpc}$ \citep{1995ApJ...448..138M}. This may be caused
by the model in our simulations not driving enough turbulent pressure, and is an
interesting avenue of further investigation.}
